### 2022-01-20 papers/paper/preprint.tex
Send to Klaus for comments / feedback

\Cref{fig:boxplots} shows the \glspl{pdf} of mean sea level in 2100 under each of the eight models considered: four emissions pathways (\gls{rcp} scenarios) times two models of ice sheet dynamics.
Variation between different \glspl{pdf} is dominated by the \gls{rcp} 8.5 scenario with fast ice sheet dynamics \citep[see][for a discussion of these dynamics]{wong_brick0.2:2017}.
This is also the \gls{pdf} with the greatest within-model variance.
\begin{figure}
    \centering
    \includegraphics[width=5in]{msl_boxplots.pdf}
    \caption{
        Sea level rise projections use the BRICK model \citep{wong_brick0.2:2017,ruckert_coastal:2019}.
        We consider \emph{eight time-dependent PDFs of sea level rise}: four \gls{rcp} scenarios $\times$ two parameterizations of ice sheet processes.
    }\label{fig:boxplots}
\end{figure}

@@

To assess the performance of a given decision for a specific \gls{sow}, we calculate three metrics for each \gls{sow}.
\begin{enumerate}
    \item The first metric considered is ``upfront cost,'' which reflects the cost of elevating a house. Following \citet{zarekarizi_suboptimal:2020}, we use estimates of construction cost from the Coastal Louisiana Risk Assessment \citep{fischbach_clara:2012}. We normalize this cost by house value.\james{Normalize!}
    \item The second metric is the lifetime expected damages (\cref{eq:led})
    \item The third metric is lifetime expected costs, which is the sum of lifetime expected damages and upfront costs
    \item The third metric is the expected benefit-to-cost ratio.  We define this ratio in terms of the ratio of construction cost to damages averted relative to not elevating at all:
          \begin{equation}
              \mathrm{BCR}(\Delta h) = \begin{cases} \Delta h = 0 & 1 \\ \Delta h \neq 0 & \frac{\mathbb{E}[d_t | \Delta h = 0] - \mathbb{E}[d_t | \Delta h = \Delta h]}{C(\Delta h)}\end{cases}
          \end{equation}
\end{enumerate}

\section{Exploring possible states of the world}\label{sec:multiple-simulation}

The literature on decision making under deep uncertainty \citep[see][]{marchau:2019} offers some insight as to how to identify decisions that perform well over many plausible \acrfullpl{sow}.

The first that we consider is exploratory modeling.
In general, we consider $J$ simulated \glspl{sow} $\qty{s_1, \ldots, S_J}$ and $I$ possible decisions $\qty{x_1, \ldots, x_I}$.
As described in the previous section, these $J$ \glspl{sow} represent time series of mean sea level and the $I$ decisions represent how high to elevate the house.
For each combination of these, we calculate the vector of metrics described in \cref{sec:sow-metrics}: $u_{ij} = f(x_i, s_j)$ using the system model $f$, which includes storm surge (\cref{sec:storm-surge}), damage (\cref{sec:ead,sec:led}), and calculation of additional metrics (\cref{sec:sow-metrics}).
This framework is illustrated in \cref{fig:flowchart} inside the box labeled Section 3\klaus{Any suggestions for how I can draw these regions better?}; we return in \cref{sec:multiple-pdf,sec:synthesizing} to add additional steps to the model.

\begin{figure}
    \centering
    \includegraphics[width=4in]{bayes-rdm.pdf}
    \caption{
        Outline of the generally applicable decision theoretic framework developed.
        We begin in \cref{sec:multiple-simulation} by presenting results using exploratory modeling, \ie nodes  (a), (b), and (c).
        In \cref{sec:multiple-pdf} we discuss nodes (d) and (e) to understand scenario-conditional probability distributions.
        Finally in \cref{sec:synthesizing} we add nodes (f) and (g) to synthesize across multiple \glspl{pdf}.
    }\label{fig:flowchart}
\end{figure}

Analysis of these $u_{ij}$ sheds light on the question: ``how well does a given decision perform under different possible futures?''
\Cref{fig:scenario-map} shows each possible future as a single dot for each of several possible values for $\Delta h$.
On the $y$ axis is expected lifetime costs (see \cref{sec:sow-metrics}).
On the $x$ axis is mean sea level in 2100, which is an interpretable 1-dimensional projection of the \glspl{sow}.
Although our model for expected discounted total costs is deterministic, points with similar $x$-values may have different $y$-values because their sea levels before 2100 can differ.

\begin{figure}
    \includegraphics[width=\textwidth]{scenario_maps.png}
    \caption{
        Scenario maps: one dot represents one \gls{sow}.
    }\label{fig:scenario-map}
\end{figure}

\Cref{fig:scenario-map} shows that the best outcome is when $\Delta h = 0$ and when \gls{slr} is negligible.
However, the worst outcome is also when $\Delta h = 0$ and when \gls{slr} is substantial.
As $\Delta h$ increases, the construction cost increases but the variability between different \glspl{sow} decreases, up to a point.
\emph{No decision dominates} any other, including $\Delta h = 0$, in the formal sense of being optimal over all \glspl{sow}.

\section{The multiple PDF problem}\label{sec:multiple-pdf}

@@

An alternative framework is to interpret the \glspl{sow} as draws from each of eight \glspl{pdf}.
This has the approach of a probabilistic interpretation: \emph{conditional on a particular model} (\gls{rcp} scenario and ice sheet model structure), we can view corresponding \glspl{sow} as IID draws from the distribution of outcomes.

Some general notation is shown in \cref{fig:flowchart} (additional terms are added in \cref{sec:synthesizing}).
We have $K=8$ models of sea level rise, which we refer to as $\qty{\mathcal{M}_1, \ldots, \mathcal{M}_K}$.

\subsection{Metrics}

This allows us to reason formally about the \gls{pdf} of outcomes for each candidate decision, conditional on a model.
We can use these \glspl{pdf} of outcomes to calculate metrics describing the performance of decisions.

Any optimal strategy or Pareto frontier is conditional upon an (explicit or implicit) model of future outcomes.

@@

@@

Weights assigned to PDFs or simulations, \textbf{including implicit uniform weights}, should be communicated transparently to facilitate critique and improvement.\james{TODO: create a figure showing expected outcomes if you design for scenario $x$ and get scenario $y$}

\section{Synthesizing across PDFs for decision relevance}\label{sec:synthesizing}

\subsection{Methods}

While comparing results across many PDFs is a valuable exploratory exercise (see, \eg, \cref{fig:tradeoffs}), providing end users (\eg, households practicing engineers, and planning departments of local governments) with many PDFs may lead to confusion, inconsistency, and potentially liability \citep[see][]{schneider_dangerous:2001,schneider_scenarios:2002}.

Our approach to synthesizing PDFs is designed for the common case of assessing decisions using simulations (SOWs) from each of $K$ PDFs.
A system model $(f)$ quantifies the performance $(u)$ of a decision ($x$) under a single SOW ($s$).
To synthesize, we weight PDFs using an approach based on Bayesian Model Averaging \citep{wong_surge:2018,Yao:2018bu}.

\subsection{Findings}

\begin{figure}
    \centering
    \includegraphics[width=6in]{inference_weights.pdf}
    \caption{
        The weights assigned to each PDF (from \cref{fig:boxplots}) under each prior considered.
    }
\end{figure}
``Pessimistic'' (``Optimistic'') prior heavily weights \gls{rcp} 8.5 (2.6), which is unlikely given current policies \citep{hausfather_scenarios:2020}.

\begin{figure}
    \centering
    \includegraphics[width=3in]{lsl_priors.pdf}~
    \includegraphics[width=3in]{tradeoffs_height_totalcost_byprior.pdf}
    \caption{
        The prior model averaging approach (\cref{fig:flowchart}), uses a probability distribution representing subjective belief to average insights across each PDF available.
        Alternative priors can provide robustness checks.
    }
\end{figure}

To summarize:
\begin{itemize}
    \item Natural extensions to Bayesian updating
    \item Belief $p(s)$ can't be ``right''  \citep{gelman_workflow:2020,gelman_philosophy:2013} or ``neutral'' \citep{quinn_exploratory:2020}
    \item Instead, we can ask \textbf{what assumptions are different priors consistent with?}
\end{itemize}

This didactic example illustrates a need for better synthesis and communication of deep uncertainties for decision making.
\textbf{\scshape let's collaborate on:}
\begin{itemize}
    \item More complex models to capture more relevant metrics
    \item Better models of nonstationary hazards
    \item Interacting, sequential decisions
\end{itemize}

@@

@@

\section{Conclusions}

\begin{enumerate}
    \item We started with the problem of ``which scenario should we design to?'' We then devised a cop-out: design to a weighted combination of all the scenarios. (So how should we wight the scenarios? Come up with a model $p(\Omega)$ that tells you.)
    \item There is no objective way to choose $p(\Omega)$ because we don't have data on the future!
    \item We can't get around from choosing $p(\Omega)$ implicitly\footnote{I'm not sure we have demonstrated this rigorously, or whether we want to argue it, but I think there's a way to frame this point that is valid and helpful}
    \item Ultimately, engineering design needs to consider not only how to weight different future scenarios, but also which metrics are important, how risk aversion should be addressed, \etc.
    \item We used a didactic case study to present a toolkit (decision framework, melding priors, prior over return levels) for making transparent and critique-friendly assessments.
\end{enumerate}

\subsection*{Supplementary Materials}

\section{Old material}

\clearpage
\newpage

>>>>

\Cref{fig:msl-boxplots} shows the \glspl{pdf} of mean sea level in 2100 under each of the eight models considered: four emissions pathways (\gls{rcp} scenarios) times two models of ice sheet dynamics.
Variation between different \glspl{pdf} is dominated by the \gls{rcp} 8.5 scenario with fast ice sheet dynamics \citep[see][for a discussion of these dynamics]{wong_brick0.2:2017}.
This is also the \gls{pdf} with the greatest within-model variance.
\begin{figure}
    \centering
    \includegraphics[width=5in]{msl_boxplots.pdf}
    \caption{
        Sea level rise projections use the BRICK model \citep{wong_brick0.2:2017,ruckert_coastal:2019}.
        We consider \emph{eight time-dependent PDFs of sea level rise}: four \gls{rcp} scenarios $\times$ two parameterizations of ice sheet processes.
    }\label{fig:msl-boxplots}
\end{figure}

@@

To assess the performance of a given decision for a specific \gls{sow}, we calculate the following metrics \emph{for each decision-\gls{sow} combination}.
\begin{description}
    \item[upfront cost] reflects the cost of elevating a house. Following \citet{zarekarizi_suboptimal:2020}, we use estimates of construction cost from the Coastal Louisiana Risk Assessment \citep{fischbach_clara:2012}. We normalize this cost by house value.\james{Normalize!}
    \item[lifetime expected damages] is discussed in \cref{sec:led}
    \item[lifetime expected costs] is the sum of lifetime expected damages and upfront costs
    \item[the expected benefit-to-cost ratio] is defined as the ratio of construction cost to damages averted, relative to not elevating at all:
        \begin{equation}
            \mathrm{BCR}(\Delta h) = \begin{cases} \Delta h = 0 & 1 \\ \Delta h \neq 0 & \frac{\mathbb{E}[d_t | \Delta h = 0] - \mathbb{E}[d_t | \Delta h = \Delta h]}{C(\Delta h)}\end{cases}
        \end{equation}
\end{description}
In \cref{sec:multiple-simulation} we introduce the notation $u$ for these metrics.

\subsection{Decision analytical framework}

In \cref{fig:flowchart} we introduce a general notation for model-based decision analysis which we develop incrementally.
We consider $J$ \glspl{sow} representing time series of mean sea level and $I$ discrete decisions representing the choice for how high to elevate the house $\Delta h$.
For each combination of these, we calculate the vector of metrics described in \cref{sec:sow-metrics}, which we denote $u_{ij} = f(x_i, s_j)$, using a system model $f$ (box c).
This system model represents storm surge, building costs, and damages to output the metrics $u$ (which in this case is a vector).
In \cref{sec:multiple-simulation} we consider ``the multiple \gls{pdf} problem'' by introducing boxes (d) and (e).
Finally in \cref{sec:synthesizing} we introduce box (f) as a tool for synthesizing uncertainty across the multiple \glspl{pdf}.\klaus{Any feedback on the is figure and/or section?}

\begin{figure}
    \centering
    \includegraphics[width=4in]{bayes-rdm.pdf}
    \caption{
        Outline of the generally applicable decision theoretic framework developed.
        Boxes are labeled in the order in which they are presented in the text: we begin in \cref{sec:multiple-simulation} using a lens of exploratory modeling, \ie boxes  (a), (b), and (c), to analyze the elevation problem.
        In \cref{sec:multiple-pdf} we discuss Boxes (d) and (e) to understand scenario-conditional probability distributions and the ``multiple \acrshort{pdf} problem''.
        Finally in \cref{sec:synthesizing} we add boxes (f) and (g) to synthesize across multiple \glspl{pdf}.
    }\label{fig:flowchart}
\end{figure}

\section{Exploratory analysis}\label{sec:multiple-simulation}

The literature on decision making under deep uncertainty \citep[see][]{marchau:2019} offers some insight as to how to identify decisions that perform well over many plausible \acrfullpl{sow}.
The first that we consider is exploratory modeling, which sheds light the questions: ``how well does a given decision perform under different possible futures, and to which possible futures are different decisions vulnerable?''

\Cref{fig:scenario-map} shows each possible future as a single point for each of several values of $\Delta h$.\klaus{Would it be better here to have a figure that has $\Delta h$ on the $y$ axis and uses expected lifetime cost to color the points?}
On the $y$ axis is expected lifetime costs (see \cref{sec:sow-metrics}).
On the $x$ axis is mean sea level in 2100, which is an interpretable 1-dimensional projection of the \glspl{sow}.
Although our model for expected discounted total costs is deterministic, points with similar $x$-values may have different $y$-values because their sea levels before 2100 can differ (\ie, the 1-dimensional projection of the \glspl{sow} does not represent all variance between them).

\begin{figure}
    \includegraphics[width=\textwidth]{scenario_maps.png}
    \caption{
        Scenario maps: one dot represents one \gls{sow}.
        Some work is still needed -- I think that changing to four values of $\Delta h$ and showing two or three different values of $h_0$ might be useful (alternatively we could vary the discount rate $\gamma$).
        Also need to rescale the $y$-axis by house value.
        It would also be cool to create an interactive online version of this figure that lets you scroll over a particular dot and learn which scenario it's from!
        %TODO
    }\label{fig:scenario-map}
\end{figure}

The exploratory modeling approach shown in \cref{fig:scenario-map} shows that shows that the best outcome is when $\Delta h = 0$ and when \gls{slr} is negligible, but the worst outcome is also when $\Delta h = 0$ and when \gls{slr} is substantial.
As $\Delta h$ increases, the construction cost increases but the variability between different \glspl{sow} decreases, up to a point.
\emph{No decision dominates} any other, including $\Delta h = 0$, in the formal sense of being optimal over all \glspl{sow}.
\james{Revisit this paragraph once changes are made to \cref{fig:scenario-map}.}

\section{Scenario-conditional probabilistic analysis: the multiple PDF problem}\label{sec:multiple-pdf}

@@

An alternative interpretation of the available \glspl{sow} is as IID draws from each of eight \glspl{pdf} of sea level rise, as shown in \cref{fig:msl-boxplots}.
This has the approach of a probabilistic interpretation: \emph{conditional on a particular model} (\gls{rcp} scenario and ice sheet model structure), we can view corresponding \glspl{sow} as IID draws from the distribution of outcomes.

A more formal notation is introduced in boxes (d) and (e) of \cref{fig:flowchart}.
Specifically, for each of $K$ models (box d), which here are our eight models for \gls{slr},\james{need to go through whole document and be consistent about MSL, SLS, SRL, RSLR, \etc} the samples of metrics are taken to be IID samples from the distribution of outcomes (box e).
Since we define these models to estimate $p(\Omega)$, our models $M_1, \ldots, M_K$ return a probability of $1 / J_K$ for each of the $J_K$ simulations from the $K$th model, and $0$ for simulations from all other models.
We can then use this conditional distribution over outcomes to create metrics that depend only on the decision, such as averages or quantiles of outcomes.

@@

For example, \cref{fig:tradeoffs}(a) plots the expected lifetime cost\james{update figure} as a function of $\Delta h$\james{Add $\Delta h$ to the plot} for four of the eight models available.
Similarly, \cref{fig:tradeoffs} plots the 80\% confidence interval width (\ie, the 90th percentile minus the 10th percentile) of lifetime cost.
This figure shows that for small $\Delta h$, expected costs are low under optimistic models (\eg, \gls{rcp} 2.6 with slow ice sheet dynamics) and high under pessimistic models (\eg, \gls{rcp} 8.6 with fast ice sheet dynamics).
Consistent with \cref{fig:scenario-map}, the variability of lifetime costs increases as $\Delta h$ increases.
Once $\Delta h$ reaches \SIrange[]{3}{7}{ft}, depending on the model considered, construction costs start to dominate flood losses, and thus higher values of $\Delta h$ increase average lifetime costs.

Calculating either of the quantities shown in \cref{fig:tradeoffs} \emph{requires synthesizing across \glspl{sow}}.
However, these metrics are necessarily dependent on the model used (\ie, \gls{rcp} scenario and model of ice sheet dynamics).
This means that any assessment of decision performance (\eg, an optimal strategy, a Pareto frontier, or a cost-benefit analysis) is conditional upon an (explicit or implicit) model of future outcomes.
Where these models are implicit, they should be made more explicit to facilitate iterative model critique and improvement.

Second, this approach presents what we call ``the multiple \gls{pdf} problem'' because it leaves decision makers with many probability distributions to choose from
Cite \citet{sharma_rcp:2021} as another example.
Add a sentence or two explaining why this is a problem for decision makers\ldots\james{Need to bring in a bit of discussion from \citet{schneider_scenarios:2002} and from engineering docs (ASCE, FEMA, \ldots).}\klaus{Would appreciate your help putting together a succinct summary of the multiple \gls{pdf} problem}

\section{Synthesizing PDFs for decision relevance}\label{sec:synthesizing}

Motivated by the multiple \gls{pdf} problem, we develop in this section a framework for synthesizing information across \glspl{pdf} using subjective Bayesian modeling.

Specifically, we frame the set of \glspl{sow} through a sampling lens and consider the possibility that the distribution from which they are sampled, $p_\textrm{empirical}(\Omega)$, does not reflect our belief about their true distribution, $p_\mathrm{true}(\Omega)$.
Often this is by design: exploratory modeling emphasizes the value of sampling low-probability futures as a way to learn about the system and develop insight \citep{bankes:1993}.
This is analagous to the deliberate over- or under-sampling of certain groups in survey design, and so following standard practice in survey design we develop a re-weighting approach to correct for the over- or under-sampling of different regions of the survey space.

To calculate these weights, we apply a grid-based discretization scheme.
First, we project the \glspl{sow} $s_1, \ldots, s_J$ onto a one-dimensional space, which we denote $\psi_1, \ldots, \psi_J$.
As before, we take this space to be the mean sea level in 2100.
Without loss of generality, we assume the $\psi_j$ to be sorted from least to greatest so that $\psi_{j-1} \leq \psi_j$, ($j \neq 1$).
This allows us to simplify $p_\mathrm{true}(s_j) = p_\mathrm{true}(\psi_j)$.\klaus{This notation seems bad, suggestions?}
Defining $F_\mathrm{true}(s)$ to be the cumulative distribution corresponding to $p_\mathrm{true}$, \ie
$$F_\mathrm{true}(s) = \int_{-\infty}^{s'} p_\mathrm{true}(s) \dd{s},$$
we calculate weights using \cref{eq:weights} as illustrated in \cref{fig:weighting}.
\begin{equation}\label{eq:weights}
    w_j = \begin{cases}
        j = 1     & F_\mathrm{true}\qty(\frac{1}{2}\qty[\psi_1 + \psi_2])                                                                   \\
        1 < j < J & F_\mathrm{true}\qty(\frac{1}{2}\qty[\psi_{j} + \psi_{j+1}]) - F_\mathrm{true}\qty(\frac{1}{2}\qty[\psi_{j-1} + \psi_j]) \\
        j = J     & 1 - F_\mathrm{true}\qty(\frac{1}{2}\qty[\psi_{J-1} + \psi_J]).
    \end{cases}
\end{equation}
This grid-based weighting scheme can be used with higher-dimensional projections of the scenarios, as is done for example in the joint probability method used for hurricanes \citep[see, \eg,][]{johnson_clara:2013,toro_jpm-os:2010}.

The primary difficulty with \cref{eq:weights} is that the true probability distribution $p_\mathrm{true}(\phi)$ is not only unknown but deeply uncertain.
Because it is unknown, it must be approximated with a model.
And because it is deeply uncertain, multiple models for $p_(\Omega)$ should be used.
But whereas the $M_k$ defined in \cref{sec:multiple-pdf} represented the raw input data (four \gls{rcp} scenarios times two models of ice sheet dynamics), we define the $M_k$ here to be subjective models for mean sea level in 2100.

Need a few sentences here on prior uses of expert judgement and subjective belief.\klaus{Any suggested citations?}
The key point to get across is what a subjective belief means in the Bayesian context \citep{savage:1954,gelman_philosophy:2013,gelman_subjectiveobjective:2017}.
David Spiegelhalter had a nice comment on a podcast where he explained that in medicine, there isn't a ``true'' probability that, for example, you will get cancer; this is not some real quantity that can be measured \citep[hence the famous ``probability isn't real'' admonisment of][]{definetti_probability:1972}.
Similarly, the probability distribution of sea level rise in 2100 isn't something that can be measured.
However, probability provides a clear and self-consistent mathematical language for reasoning about uncertainty, which is why we're using it.
A key advantage is that \textbf{since we can't be right, we can at least be transparent} about the assumed values of sea level in 2100, rather than hiding behind implicit assumptions.
Thus we refer to the $M_k$ here as \emph{priors} to reflect that they consistently represent our current knowledge.

\begin{figure}
    \centering
    \includegraphics[width=4in]{../img/weighting.pdf}
    \caption{
        Schematic of re-weighting scheme defined in \cref{eq:weights} for $J=4$.
        Top panel shows $p_\mathrm{true}$ and bottom panel shows $F_\mathrm{true}$.
        Vertical black lines show $\frac{1}{2}\qty[\psi_j + \psi_{j+1}]$ for $j=1, \ldots, J-1$.
        Green text shows $w_1, \ldots, w_4$ and how they are calculated from $F_\mathrm{true}$.
        Need to update this figure using real data.
        %TODO
    }\label{fig:weighting}
\end{figure}

Need to explain how we came up with our two or three subjective priors.\klaus{Would love suggestions here!}
Another advantage of this method is that it is computationally cheap to re-weight the \glspl{sow}.
Thus, exploring performance under alternative priors is computationally cheap and easy to implement.
\Cref{fig:tradeoffs} shows the priors used in panel (a) and in panel (b) shows average lifetime cost as a function of the decision ($\Delta h$) after integrating over all possible \glspl{sow} (\ie, after synthesizing the ``multiple \glspl{pdf}.'')

\begin{figure}
    \centering
    \includegraphics[width=3in]{lsl_priors.pdf}~
    \includegraphics[width=3in]{tradeoffs_height_totalcost_byprior.pdf}
    \caption{
        The prior model averaging approach (\cref{fig:flowchart}), uses a probability distribution representing subjective belief to average insights across each PDF available.
        Alternative priors can provide robustness checks.
        Need to add panel labels, update data, \etc.
        %TODO
    }\label{fig:tradeoffs}
\end{figure}

This technique can also be used as a diagnostic tool.
In \cref{fig:model-average-weights}, we can see that the ``Pessimistic'' (``Optimistic'') prior heavily weights \gls{rcp} 8.5 (2.6), which is unlikely given current policies \citep{hausfather_scenarios:2020}.\james{Discuss a bit more}

\begin{figure}
    \centering
    \includegraphics[width=6in]{inference_weights.pdf}
    \caption{
        The average weight assigned to \glspl{sow} from each model (\gls{rcp} scenario and ice sheet parameterization) for both priors considered.
        If the sampling distribution (green line) is used, then the weight assigned to each \gls{sow} is the same, regardless of whether it is over- or under-sampled.
    }\label{fig:model-average-weights}
\end{figure}

To summarize:
\begin{itemize}
    \item Natural extensions to Bayesian updating
    \item Belief $p(s)$ can't be ``right''  \citep{gelman_workflow:2020,gelman_philosophy:2013} or ``neutral'' \citep{quinn_exploratory:2020}
\end{itemize}

This didactic example illustrates a need for better synthesis and communication of deep uncertainties for decision making.

Future research needs:
\begin{itemize}
    \item More complex models to capture more relevant metrics
    \item Better models of nonstationary hazards
    \item Interacting, sequential decisions
\end{itemize}

\section{Bonus (need to sort through)}

This section is a work in progress -- it includes some text that used to be in the paper as well as some bullet points that may be useful for the discussion section.\klaus{Can you highlight any picese here that you find especially salient?}

@@

@@

Since we have priors, there are clear links to how we would update our belief (and thus decision) once more information arrives.

@@

### 2022-01-20 tikz/bayes-rdm.tex
Send to Klaus for comments / feedback

\tikzstyle{function} = [circle, draw, fill=grigio, text=rosso, minimum width=5.5em, text centered, align=center]
\tikzstyle{block} = [rectangle, draw, fill=giallo, text=nero, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{derived} = [rectangle, draw, rounded corners, fill=rosso, text=grigio, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{check} = [text=thirds, align=center]

@@

    \node [block] (decisions) at (0, 3) {
        Candidate decisions\\
        $\qty{x_1, x_2, \ldots, x_I} \in \mathcal{X}$
    };
    \node [block] at (-4, 3) (models) {
        Multiple PDFs\\
        $\qty{M_1, \ldots, M_K} \in \mathcal{M}$
    };
    \node [block] at (-4, 0) (simulations) {
        Simulated SOWs\\
        $\qty{s_1, \ldots, s_{N_k}}_k$
    };
    \path [line] (models) -- (simulations);
    \node [function] (model) at (0, 0) {
        System model\\
        $u_{ij} = f(x_i, s_j)$
    };
    \path [line] (simulations) -- (model);
    \path [line] (decisions) -- (model);

    \node [derived] (combined) at (4, -3) {
        Conditional distributions\\
        over outcomes\\
        $\hat{p} \qty(u | x_i, M_k)$
    };
    \path [line] (model) -- (combined);

    \node [function] (prior) at (-4, -3) {
        Prior\\
        over SOWs\\
        $p\qty(s)$
    };
    \node [derived] (weights) at (0, -3) {
        Model weights\\
        $w_1, \ldots, w_K$
    };
    \path [line] (simulations) -- (weights);
    \path [line] (prior) -- (weights);

    \node [derived] (aggregated) at (4, -6) {
        Aggregated distribution\\
        over outcomes\\
        $\hat{p}(u | x_i)$
    };
    \path [line] (combined) -- (aggregated);
    \path [line] (weights) -- (aggregated);
\end{tikzpicture}

>>>>

\tikzstyle{function} = [circle, draw, fill=grigio, text=rosso, minimum width=5.5em, text centered, align=center]
\tikzstyle{block} = [rectangle, draw, fill=giallo, text=nero, minimum width=6em, text centered,  minimum height=4em, align=left]
\tikzstyle{derived} = [rectangle, draw, rounded corners, fill=rosso, text=grigio, minimum width=6em, text centered,  minimum height=4em, align=left]

@@

    % label the various sections
    \path [fill=grigio!20] (-6.75, 4.8) -- (5.75, 4.8) -- (5.75, -4) -- (-6.75, -4) -- cycle;
    \node [color=thirds] (s5) at (-4, -3) {\textbf{Synthesize (\S 5)}};

    \path [fill=giallo!20] (-6.5, 4.6) -- (-6.5, -1.75) -- (5.5, -1.75) -- (5.5, 4.6) -- cycle;
    \node [rotate=0, color=thirds] (s4) at (4, 3.75) {\textbf{Condition (\S 4)}};

    \path [fill=thirds!20] (-6, -1.5) -- (2, -1.5) -- (2, 4.25) -- (-2, 4.25) -- (-2, 1.25) -- (-6, 1.25) -- cycle;
    \node [rotate=45, color=thirds] (s3) at (-1.25, 1.25) {\textbf{Explore (\S 3)}};

    \node [block, label={[]135:{\footnotesize (d)}}] at (-4, 3) (models) {
            Multiple models\\
            for~$p(\Omega | M_k)$:\\
            $\qty{M_1, \ldots, M_K}$
        };
    \node [block, label={[]135:{\footnotesize (a)}}] (decisions) at (0, 3) {
            Candidate decisions\\
            $\qty{x_1, x_2, \ldots, x_I}$
        };
    \node [block, label={[]135:{\footnotesize (b)}}] at (-4, 0) (simulations) {
            Many\\
            Simulated futures\\
            $\qty{s_1, \ldots, s_J} \in \Omega$
        };
    \path [line] (models) -- (simulations);
    \node [function, label={[]45:{\footnotesize (c)}}] (model) at (0, 0) {
            System model\\
            $u_{ij} = f(x_i, s_j)$
        };
    \path [line] (simulations) -- (model);
    \path [line] (decisions) -- (model);

    \node [derived, label={[]90:{\footnotesize (f)}}] (weights) at (0, -3) {
            Weights\\
            $w_1, \ldots, w_J$
        };
    \path [line] (simulations) -- (weights);

    \node [derived, label={[]135:{\footnotesize (e)}}] (combined) at (4, 0) {
            Conditional\\
            distribution\\
            over outcomes\\
            $\hat{p}(u | x_i, M_k)$
        };
    \path [line] (model) -- (combined);
    \path [line] (weights) -- (combined);

\end{tikzpicture}
